


% Here is an example of a list of titles that are all correctly formatted. All forms of authors and footnotes are present. 
% A label is present for each title. The author lists are formatted a couple of different ways, all of them valid. 
% Your list of titles should look like this before you submit them to the editor.

\subsection {Development of thin ion-implanted targets for precision studies \label{thintargets}}

\auth{
K. Deryckx,
B.\,M.~Freeman, 
A.~Garc\'{\i}a, 
G.\,C.~Harper, 
A.\,S.\,C.~Palmer, 
D.\,A.~Short, 
D.\,I.~Will, and 
\underline{C. Wrede}}




\subsection {Calculations of isospin symmetry breaking in nuclei \label{isospin}} 

\auth{
G.~Bertsch\footnoteAuthor[1]{Institute for Nuclear Theory and University of Washington.}, 
A.~Garc\'{\i}a, 
T.~Lesinski\footnotemarkAuthor[1], 
and 
\underline{C. Wrede}
}



\subsection{Analysis tools \label{KatrinAnalysis}}
\auth{S.~Enomoto}




\subsection {Measurement of light scattering in liquid scintillators considered for \snop 
\label{snoscint}} 
\auth{
\underline{T.\,J.~Major}
and 
N.\,R.~Tolich
}



%You must use \subsecmathbold in title if you use math-mode text in title.

\subsecmathbold {Development of a $^{114m}$In source of conversion electrons \label{114mIn}}

\auth{B.\,W.~Filippone\footnoteAuthor[1]{California Institute of Technology, Pasadena, CA.}, 
A.~Garc\'{\i}a, 
G.\,C.~Harper, 
S.~Lassell\footnoteAuthor[2]{North Carolina State University, Raleigh, NC.}, 
J.~Liu\footnotemarkAuthor[1], 
M.\,P.~Mendenhall\footnotemarkAuthor[1], 
A.\,S.\,C.~Palmer, 
R.\,W.~Pattie, Jr.\footnotemarkAuthor[2], 
D.\,I.~Will, 
\underline{C.~Wrede}, and 
A.\,R.~Young\footnotemarkAuthor[2]}




\subsecmathbold {Direct measurements $^{22}$Na($p,\gamma$)$^{23}$Mg resonances \label{resonances}}

\auth{
T.\,A.\,D.~Brown, 
L.~Buchmann\footnoteAuthor[1]{TRIUMF, Vancouver, BC V6T 2A3, Canada.}, 
J.\,A.~Caggiano\footnotemarkAuthor[1]\footnoteAuthor[2]{Presently at LLNL, Livermore, CA 94550.}, 
A.~Garcia, 
D.\,A.~Hutcheon\footnotemarkAuthor[1], 
D.\,F.~Ottewell\footnotemarkAuthor[1], 
C.~Ruiz\footnotemarkAuthor[1], 
A.\,L.~Sallaska, 
K.\,A.~Snover, 
D.\,W.~Storm,
C.~Vockenhuber\footnotemarkAuthor[1], 
and 
\underline{C.~Wrede}
}




\subsecmathbold {Electron capture on $^{116}$In and $2\beta$ decay \label{116In}} 

\auth{
A.~Algora\footnoteAuthor[1]{Instituto de F\'{\i}sica Corpuscular, University of Valencia, Valencia, Spain.}, 
J.~{\"A}yst{\"o}\footnoteAuthor[2]{Department of Physics, University of Jyv{\"a}skyl{\"a}, Jyv{\"a}skyl{\"a}, Finland.},
V.\,V.~Elomaa\footnotemarkAuthor[2],  
T.~Eronen\footnotemarkAuthor[2], 
A.~Garc\'{\i}a, 
J. Hakala\footnotemarkAuthor[2], 
V.\,S.~Kolhinen\footnotemarkAuthor[2], 
I.\,D.~Moore\footnotemarkAuthor[2], 
H.~Penttil{\"a}\footnotemarkAuthor[2], 
M.~Reponen\footnotemarkAuthor[2], 
J.~Rissanen\footnotemarkAuthor[2], 
A.~Saastamoinen\footnotemarkAuthor[2], 
S.\,K.~Sjue\footnoteAuthor[3]{TRIUMF, Vancouver, BC, Canada.}, 
H.\,E.~Swanson, 
and 
\underline{C.~Wrede}
}




\subsecmathbold {Mass of $^{31}$S using the Canadian Penning Trap \label{Penning}}

\auth
{S.~Caldwell\footnoteAuthor[1]{Department of Physics, University of Chicago, Chicago, IL, USA}\footnoteAuthor[2]{Physics Division, Argonne National Laboratory,
Argonne, IL, USA.}, 
A.~Chaudhuri\footnoteAuthor[3]{Department of Physics and Astronomy, University of Manitoba, Winnipeg, MB, Canada.}\footnotemarkAuthor[2], 
J.\,A.~Clark\footnotemarkAuthor[2], 
C.\,M.~Deibel\footnoteAuthor[4]{Joint Institute for Nuclear Astrophysics, Michigan
State University, East Lansing, MI, USA.}\footnotemarkAuthor[2]\footnoteAuthor[5]{Co-spokesperson for Argonne-ATLAS Experiment 1259.}, 
J.~Fallis\footnotemarkAuthor[3]\footnotemarkAuthor[2], 
A.~Garc\'{\i}a, 
S.~Gulick\footnoteAuthor[6]{Department of Physics, McGill University, Montreal, QC, Canada.}, 
D.~Lascar\footnoteAuthor[7]{Department of Physics and Astronomy, Northwestern University, Evanston, IL, USA.}\footnotemarkAuthor[2], 
G.~Li\footnotemarkAuthor[6]\footnotemarkAuthor[2], 
G.~Savard\footnotemarkAuthor[2]\footnotemarkAuthor[1], 
K.\,S.~Sharma\footnotemarkAuthor[3], 
M.~Sternberg\footnotemarkAuthor[1]\footnotemarkAuthor[2], 
T.~Sun\footnotemarkAuthor[2], 
J.~Van Schelt\footnotemarkAuthor[1]\footnotemarkAuthor[2], and 
\underline{C.~Wrede}\footnotemarkAuthor[5]}




\subsecmathbold {Properties of $^{20}$Na, $^{24}$Al, $^{28}$P, $^{32}$Cl, and $^{36}$K \label{masses}}

\auth{
S.~Bishop\footnoteAuthor[1]{Physik Department, Technische Universit\"{a}t M\"{u}nchen, Garching, Germany.},
A.\,A.~Chen\footnoteAuthor[2]{Department of Physics and Astronomy, McMaster University, Hamilton, ON, Canada.}\footnoteAuthor[3]{DFG Cluster of Excellence Universe, Technische Universit\"{a}t M\"{u}nchen, Garching, Germany.},
J.\,A.~Clark\footnoteAuthor[4]{Physics Division, Argonne National Laboratory, Argonne, IL, USA.},
C.\,M.~Deibel\footnotemarkAuthor[4]\footnoteAuthor[5]{Joint Institute for Nuclear Astrophysics, Michigan State University, East Lansing, MI, USA.},
K.~Eppinger\footnotemarkAuthor[1],
T.~Faestermann\footnotemarkAuthor[1],
B.\,M.~Freeman,
A.~Garc\'{\i}a,
R.~Hertenberger\footnoteAuthor[6]{Fakult\"{a}t f\"{u}r Physik, Ludwigs-Maximilians-Universit\"{a}t M\"{u}nchen, Garching, Germany.},
R.~Kr{\"u}cken\footnotemarkAuthor[1],
O.~Lepyoshkina\footnotemarkAuthor[1],
A.~Parikh\footnotemarkAuthor[1],
G.~Rugel\footnotemarkAuthor[1],
K.~Setoodehnia\footnotemarkAuthor[2],
H.\,-F.~Wirth\footnotemarkAuthor[6], and
\underline{C.~Wrede}}




\subsecmathbold {Thermonuclear $^{25}$Al($p,\gamma$)$^{26}$Si reaction rate from $^{26}$P beta decay \label{rates}}

\auth{
J.~Brown\footnoteAuthor[1]{University of York, York, UK.}, 
R. Casten\footnoteAuthor[2]{Yale University, New Haven, CT.}, 
A.~Chen\footnoteAuthor[3]{McMaster University, Hamilton, ON.}, 
K.~Chipps\footnoteAuthor[4]{Colorado School of Mines, Golden, CO.}, 
J.~Clark\footnoteAuthor[5]{Argonne National Laboratory, Argonne, IL.},
 N.~Cooper\footnotemarkAuthor[2], 
 C.~Deibel\footnoteAuthor[6]{Joint Institute for Nuclear Astrophysics.}\footnotemarkAuthor[5], 
 A.~Garc\'{\i}a, D.~Irvine\footnotemarkAuthor[3], 
 J.~Jos{\'e}\footnoteAuthor[7]{UPC/IEEC Barcelona, Barcelona, Spain.}, 
 A.~Knecht, 
 A.~Laird\footnotemarkAuthor[1], 
 S.~Liddick\footnoteAuthor[8]{Michigan State University, East Lansing, MI.}, 
 F.~Montes\footnotemarkAuthor[8], 
 A.~ Parikh\footnoteAuthor[9]{UPC Barcelona, Barcelona, Spain.}, 
 H.~Schatz\footnotemarkAuthor[8], 
 K.~Setoodehnia\footnotemarkAuthor[3], 
 V.~Werner\footnotemarkAuthor[2], and 
 \underline{C.~Wrede}}



\subsection {Miscellaneous studies of nova nucleosynthesis \label{nova}}

\auth{\underline{C.~Wrede} and outside collaborators\footnote{~$^{23}$Mg($p,\gamma$)$^{24}$Al work: TRIUMF experiment S810, C.~Vockenhuber and U. Greife spokespersons; the collaboration is formed by approximately 30 scientists from Argonne National Lab., Univ. of British Columbia, McMaster Univ., Colorado School of Mines, Tech. Univ. M{\"u}nchen, Univ. of Northern British Columbia, Simon Fraser Univ., TRIUMF, Univ. of Washington, and Univ. Wien.}$^{,}$\footnote{~$^{31}$P($^3$He,$t$)$^{31}$S and $^{32}$S($d,t$)$^{31}$S work: A. Parikh and A.\,A.~Chen spokespersons, respectively; the collaborations are formed by approximately 20 scientists from Argonne National Lab., Ludwig-Maximilians-Univ. M{\"u}nchen, Maier-Leibnitz-Lab., McMaster Univ., Tech. Univ. M{\"u}nchen, Univ. Politecnica de Catalunya, and Univ. of Washington}$^{,}$\footnote{~$^{32}$S($p,t$)$^{30}$S work: K.~Setoodehnia, A.\,A.~Chen, J. Chen, S.\,D.~Geraedts, and D.~Kahl (McMaster Univ.); J.\,A.~Clark, C.\,M. Deibel, and P.\,D.~Parker (Yale Univ.).; D.~Seiler (Tech. Univ. M{\"u}nchen)}}


