
% Example publications list 3/19/2013 GCH

% Your publications should be formatted like the following before submitting them to 
% the editor or assistant editor. Here are some examples of publications. Full author lists 
% only, no use of et al. If one or more CENPA authors are the lead author or major  
% contributor to a paper, use \leadauthor as shown. Indicate any publication that is  
% partially or fully supported by the DOE at the end with \DOEsupport. To enumerate  
% the list, make sure \item precedes each entry. To typeset your publications list, strip 
% out all the examples in the list and insert yours in the appropriate \subsections. 
% Typeset using the file MakePublicationList.tex

\let\thefootnote\relax\footnotetext{An {\bf *} denotes a CENPA author who is the lead author of or major contributor to a publication.}
\let\thefootnote\relax\footnotetext{A {\bf \dag} denotes a publication describing work fully or partially supported by the DOE grant.}

\newcommand{\leadauthor}{{\bf *}}                   
\newcommand{\DOEsupport}{{\bf \dag}}                     
                  
\subsection{Published papers}

\raggedright

\begin{enumerate} %Published papers

\item ``Solar fusion cross sections II: the pp chain and CNO cycles,'' E.\,G.~Adelberger, A.~Garc\'{i}a, R.\,G.\,H.~Robertson, K.\,A.~Snover, A.\,B.~Balantekin, K.\,M.~Heeger, M.\,J.~Ramsey-Musolf, D.~Bemmerer, A.~Junghans, C.\,A.~Bertulani, J.-W.~Chen, H.~Costantini, P.~Prati, M.~Couder, E.~Uberseder, M.~Wiescher, R.~Cyburt,  B.~Davids, S.\,J.~Freedman, M.~Gai, D.~Gazit, L.~Gialanella, G.~Imbriani, U.~Greife, M.~Hass, W.\,C.~Haxton, T.~Itahashi, K.~Kubodera, K.~Langanke, D.~Leitner, M.~Leitner, P.~Vetter, L.~Winslow, L.\,E.~Marcucci, T.~Motobayashi, A.~Mukhamedzhanov, R.\,E.~Tribble, K.\,M.~Nollett, F.\,M.~Nu\~{n}es, T.-S.~Park, P.\,D.~Parker, R.~Schiavilla, E.\,C.~Simpson, C.~Spitaleri, F.~Strieder, H.-P.~Trautvetter, K.~Suemmerer, and S.~Typel,  Rev. Mod. Phys. {\bf 83}, 195 (2011).\DOEsupport

\item ``Four methods for determining the composition of trace radioactive surface contamination of low-radioactivity metal,''  H.\,M.~O'Keeffe, T.\,H.~Burritt, B.\,T.~Cleveland, G.~Doucas, N.~Gagnon, N.\,A.~Jelley, C.~Kraus, I.\,T.~Lawson, S.~Majerus, S.\,R.~McGee, A.\,W.~Myers, A.\,W.\,P.~Poon, K.~Rielage, R.\,G.\,H.~Robertson, R.\,C.~Rosten, L.\,C.~Stonehill, B.\,A.~VanDevender\leadauthor, T.\,D.~Van Wechel, Nuclear Inst. and Methods in Physics Research, A~{\bf 659} (2011), 182; arXiv: 1103.5788 (2011).\DOEsupport

\item ``Full simulation of the Sudbury Neutrino Observatory proportional counters,'' B.~Beltran, H.~Bichsel, B.~Cai, G.\,A.~Cox, H.~Deng, J.~Detwiler, J.\,A.~Formaggio, S.~Habib, A.\,L.~Hallin, A.~Hime, M.~Huang, C.~Kraus, H.\,R.~Leslie, J.\,C.~Loach, R.~Martin, S.~McGee, M.\,L.~Miller, B.~Monreal, J.~Monroe, N.\,S.~Oblath\leadauthor, S.\,J.\,M.~Peeters, A.\,W.\,P.~Poon, G.~Prior, K.~Rielage, R.\,G.\,H.~Robertson, M.\,W.\,E.~Smith, L.\,C.~Stonehill, N.~Tolich, T.~Van~Wechel, H.~Wan~Chan~Tseung, J.~Wendland, J.\,F.~Wilkerson, and A.~Wright, New J. Phys. {\bf 13}, 073006 (2011).\DOEsupport

\item ``Production of ultracold neutrons from cryogenic $^2$H$_2$, O$_2$, and C$_2$H$_4$ converters,'' F.~Atchison, B.~Blau, K.~Bodek, B.~van~den~Brandt, T.~Bry\'{s}, M.~Daum, P.~Fierlinger, P.~Geltenbort, P.~Hautle, R.~Henneck, S.~Heule, A.~Holley, M.~Kasprzak, K.~Kirch, A.~Knecht, J.\,A.~Konter, M.~Ku\'{z}niak, C.-Y.~Liu, A.~Pichlmaier, C.~Plonka, Y.~Pokotilovski, A.~Saunders, D.~Tortorella, M.~Wohlmuther, A.\,R.~Young, J.~Zejma, and G.~Zsigmond, Eur. Phys. Lett {\bf 95}, 12001 (2011).

\item ``Performance of a TiN-coated monolithic silicon pin-diode array under mechanical stress,'' B.\,A.~VanDevender\leadauthor, L.\,I.~Bodine\leadauthor, A.\,W.~Myers, J.\,F.~Amsbaugh, M.\,A.~Howe, M.\,L.~Leber, R.\,G.\,H.~Robertson, K.~Tolich, T.\,D.~Van Wechel, B.\,L.~Wall, Nucl. Instrum. Methods in Phys. Research A~{\bf 673} 46 (2012).\DOEsupport 


\newpage
\let\thefootnote\relax\footnotetext{An {\bf *} denotes a CENPA author who is the lead author of or major contributor to a publication.}
\let\thefootnote\relax\footnotetext{A {\bf \dag} denotes a publication describing work fully or partially supported by the DOE grant.}

\item ``Picoradian deflection measurement with an interferometric quasi-autocollimator using weak value amplification,'' M.\,D.~Turner, C.\,A.~Hagedorn\leadauthor, S.~Schlamminger, and J.\,H.~Gundlach\leadauthor, Opt. Lett. {\bf 36}, 1479-1481 (2011); arXiv:1103.4426. 
  
\item ``Upgraded photon calorimeter with integrating readout for Hall A Compton Polarimeter at Jefferson Lab,'' M.~Friend, D.~Parno, F.~Benmokhtar, A.~Camsonne, M.~Dalton, G.\,B.~Franklin, V.~Mamyan, R.~Michaels, S.~Nanda, V.~Nelyubin, K.~Paschke, B.~Quinn, A.~Rakhman, P.~Souder, A.~Tobias, Nucl. Instrum. Methods  A {\bf 676}, 96 (2012). 

\item  ``Design and performance of the ADMX SQUID-based microwave receiver,'' S.\,J.~Asztalos, G.~Carosi, C.~Hagmann, D.~Kinion, K.~van Bibber, M.~Hotz, L.\,J~Rosenberg\leadauthor, G.~Rybka, A.~Wagner, J.~Hoskins, C.~Martin, N.\,S.~ Sullivan, D.\,B.~Tanner, R.~Bradley, J.~Clarke,  Nucl. Instrum. Methods A  {\bf  656}, 39 (2011).\DOEsupport 

\item ``Search for nonvirialized axionic dark matter,'' J.~Hoskins, J.~Hwang, C.~Martin, P.~Sikivie, N.~Sullivan, D.\,B.~Tanner, M.~Hotz, L.\,J~Rosenberg, G.~Rybka, A.~Wagner, S.\,J.~Asztalos, G.~Carosi, C.~Hagmann, D.~Kinion, K.~van Bibber, R.~Bradley, J.~Clarke, Phys. Rev. D {\bf  84}, 121302(R) (2011).\DOEsupport 

\item ``Comparing the same-side `ridge' in CMS p-p angular correlations to RHIC p-p data,''  T.\,A.~Trainor\leadauthor~and D.\,T.~Kettler, Phys. Rev. C {\bf 84}, 024910 (2011).\DOEsupport 

\end{enumerate} %Published papers

%
%
%
\subsection{Invited talks and conference presentations}
%
%
%

\begin{enumerate} %Invited talks and conference presentations

\item ``Catching up with the neutrino,''  R.\,G.\,H.~Robertson\leadauthor, Colloquium, Mississippi State University, November 7, 2011.\DOEsupport

\item ``Catching up with the neutrino,'' R.\,G.\,H.~Robertson, Invited talk, Symposium on Electroweak Nuclear Physics, Duke University, Durham, NC, March 8 -- 9, 2012.

\item ``Weighing neutrinos: What is the mass scale?''  R.\,G.\,H.~Robertson, Invited talk, ``Fundamental Physics at the Intensity Frontier'' Workshop, Washington, DC, \\ November 30 -- December 2, 2011.

\item ``University of Washington Lab Report to SNEAP 2011,'' N.\,M.~Boyd\leadauthor, T.\,M.~Cope, G.\,C.~Harper, D.\,A.~Peterson, D.\,A.~Short, S.\,P.\,R.~Steininger, T.\,D.~VanWechel, and D.\,I.~Will, October, 2011, SNEAP 2011, Oak Ridge National Laboratory, Knoxville, TN.\DOEsupport 

\item ``Muon Capture on the Proton and Determination of the Nucleon's Pseudoscalar Form Factor g$_P$,'' P.~Winter\leadauthor, Invited talk at the 19th Particles and Nuclei International Conference (PANIC11),  MIT, Cambridge, MA, July 24th -- 29th, 2011.

\end{enumerate} %Invited talks and conference presentations

\newpage
\let\thefootnote\relax\footnotetext{An {\bf *} denotes a CENPA author who is the lead author of or major contributor to a publication.}
\let\thefootnote\relax\footnotetext{A {\bf \dag} denotes a publication describing work fully or partially supported by the DOE grant.}

%
%  
%
\subsection{Abstracts and contributed talks}
%
%  
%
\begin{enumerate} %Abstracts and contributed talks

\item ``Stripper Foil Longevity,'' N.\,M.~Boyd\leadauthor, October, 2011, SNEAP 2011, Oak Ridge National Laboratory, Knoxville, TN.\DOEsupport

\end{enumerate} %Abstracts and contributed talks

%
%  
%
\subsection{Papers submitted or to be published}
%
%
%
\begin{enumerate} %Papers submitted or to be published 

\item ``Decay studies for neutrino physics: Electron capture decays of \iso{100}{Tc} and \iso{116}{In},'' A.~Garc{\'i}a, S.~Sjue, E.~Swanson, C.~Wrede, D.~Melconian, A.~Algora, I.~Ahmad, Hyperfine Interact., in press.



\item ``Search for time-reversal symmetry breaking in neutron beta decay,'' A.~Garc\'{\i}a, T.\,E.~Chupp, R.\,L.~Cooper, K.\,P.~Coulter, S.\,J.~Freedman, B.\,K.~Fujikawa, G.\,L.~Jones, H.\,P.~Mumm, J.\,S.~Nico, A.\,K.~Thompson, C.\,A.~Trull, F.\,E.~Wietfeldt, J.\,F.~Wilkerson, Proceedings of PAVI11, the 5th International Workshop.

\item ``Final Analysis of Solar Neutrino Data from the Sudbury Neutrino Observatory,'' B.~Aharmim, S.\,N.~Ahmed, A.\,E.~Anthony, N.~Barros, E.\,W.~Beier, A.~Bellerive, B.~Beltran, M.~Bergevin, S.\,D.~Biller, K.~Boudjemline, M.\,G.~Boulay, T.\,H.~Burritt, B.~Cai, Y.\,D.~Chan, D.~Chauhan, M.~Chen, B.\,T.~Cleveland, G.\,A.~Cox, X.~Dai, H.~Deng, J.~Detwiler, M.~DiMarco, P.\,J.~Doe, G.~Doucas, P.-L.~Drouin, C.\,A.~Duba, F.\,A.~Duncan, M.~Dunford, E.\,D.~Earle, S.\,R.~Elliott, H.\,C.~Evans, G.\,T.~Ewan, J.~Farine, H.~Fergani, F.~Fleurot, R.\,J.~Ford, J.\,A.~Formaggio, N.~Gagnon, J.\,TM.~Goon, K.~Graham, E.~Guillian, S.~Habib, R\,L.~Hahn, A.\,L.~Hallin, E.\,D.~Hallman, P.\,J.~Harvey, R.~Hazama, W.\,J.~Heintzelman, J.~Heise, R.\,L.~Helmer, A.~Hime, C.~Howard, M.\,A.~Howe, M.~Huang, B.~Jamieson, N.\,A.~Jelley, K.\,J.~Keeter, J.\,R.~Klein, L.\,L.~Kormos, M.~Kos, C.~Kraus, C.\,B.~Krauss, T.~Kutter, C.\,C.\,M.~Kyba, J.~Law, I.\,T.~Lawson, K.\,T.~Lesko, J.\,R.~Leslie, I.~Levine, J.\,C.~Loach, R.~MacLellan, S.~Majerus, H.\,B.~Mak, J.~Maneira, R.~Martin, N.~McCauley, A.\,B.~McDonald, S.~McGee, M.\,L. Miller, B. Monreal, J. Monroe, B. Morissette, B.\,G.~Nickel, A.\,J. Noble, H.\,M. O'Keeffe, N.\,S.~Oblath, G.\,D.~Orebi Gann, S.\,M.~Oser, R.\,A.~Ott, S.\,J.\,M.~Peeters, A.\,W.\,P.~Poon, G.~Prior, S.\,D.~Reitzner, K.~Rielage, B.\,C.~Robertson, R.\,G.\,H.~Robertson, R.\,C.~Rosten, M.\,H.~Schwendener, J.\,A.~Secrest, S.\,R.~Seibert, O.~Simard, P.~Skensved, T.\,J.~Sonley, L.\,C.~Stonehill, G.~Tesic, N.~Tolich, T.~Tsui, R.~Van~Berg, B.\,A.~VanDevender, C.\,J.~Virtue, B.\,L.~Wall, D.~Waller, H.~Wan~Chan~Tseung, D.\,L.~Wark, N.~West, J.\,F.~Wilkerson, J.\,R.~Wilson, J.\,M.~Wouters, A.~Wright, M.~Yeh, F.~Zhang, and K.~Zuber (SNO Collaboration) Phys. Rev. C (submitted September 5, 2011); arXiv 1109.0763. 

\item ``Glasma flux tubes vs minimum-bias jets in 2D angular correlations on $\eta$ and $\phi$,''  T.\,A.~Trainor, arXiv:1012.2373, submitted to J. Phys. G.

\end{enumerate} %Papers submitted or to be published

\newpage
\let\thefootnote\relax\footnotetext{An {\bf *} denotes a CENPA author who is the lead author of or major contributor to a publication.}
\let\thefootnote\relax\footnotetext{A {\bf \dag} denotes a publication describing work fully or partially supported by the DOE grant.}

%
%
%
\subsection{Reports and white papers}
%
%
%

\begin{enumerate} %Reports and white papers

\item ``Discovering the New Standard Model: Fundamental Symmetries and Neutrinos,''
V.~Cianciolo, A.\,B.~Balantekin, A.~Bernstein, V.~Cirigliano, M.\,D.~Cooper, D.\,J.~Dean, S.\,R.~Elliott, B.\,W.~Filippone, S.\,J.~Freedman, G.\,L.~Greene, K.\,M.~Heeger, D.\,W.~Hertzog\leadauthor, B.\,R.~Holstein, P.~Huffman, T.~Ito, K.~Kumar, Z.-T.~Lu, J.\,S.~Nico, G.\,D.~Orebi~Gann, K.~Paschke, A.~Piepke, B.~Plaster, D.~Pocanic, A.\,W.\,P.~Poon, D.\,C.~Radford, M.\,J.~Ramsey-Musolf, R.\,G.\,H.~Robertson\leadauthor, G.~Savard, K.~Scholberg, Y.~Semertzidis, J.\,F.~Wilkerson, Report of the Fundamental Symmetries and Neutrinos Workshop, August 10--11, 2012, Chicago, IL (Submitted Dec 20, 2012 arXiv:1212.5190.

\end{enumerate} %Reports and white papers

%
%
%
\subsection{Book Publications}
%
%
%

``Faster-than-Light Implications of Quantum Entanglement and Nonlocality,'' John~G.~Cramer, Chapter 16 of \emph{Frontiers of Propulsion Science}, Eds. Marc~G.~Millis and Eric~W.~Davis, American Institute of Aeronautics and Astronautics
(2009), ISBN-10: 1-56347-956-7, ISBN-13: 978-1-56347-956-4.

``The Transactional Interpretation of Quantum Mechanics,'' John G.~Cramer, book
chapter published in \emph{Compendium of Quantum Physics: Concepts, Experiments,
History, and Philosophy}, Eds. Daniel Greenberger, Klaus Hentschel and Friedel
Weinert, Springer-Verlag Berlin Heidelberg (2009), ISBN 978-3-540-70622-9.

%
%
%
\subsection{Patents}
%
%
%

``Interferometric Quasi-Autocollimator,'' U.S. Patent Application No. 13/426,309, unpublished (filing date Mar. 21, 2012) (M.\,D.~Turner, J.\,H.~Gundlach, C.\,A.~Hagedorn, and S.~Schlamminger, applicants). 

%
%
%
\subsection{Ph.D. degrees granted}
%
%
%
{\it Searching for neutrinoless double-beta decay of germanium-76 in the presence of backgrounds}, Alexis\,G.~Schubert (December, 2013).

{\it Karlsruhe tritium experiment detector system commissioning and in-situ PIN diode array dead layer measurement}, Brandon\,L.~Wall (March, 2013).
